### 2021-11-26 paper/output/document/threeflags.tex
and that's chapter 4

Though Kantians study all formulations of the categorical imperative, Kant argues in Groundwork 
that the three formulations of the categorical imperative are equivalent \cite{groundwork}. While this 
argument is disputed \cite{sepkant}, for those who believe it, the
stakes for my choice of the FUL are greatly reduced. If all formulations are equivalent, then a formalization of the FUL
lends the exact same power as a formalization of the second or third formulation of the categorical 
imperative. In fact, future work could formalize the other formulas and try to prove that they 
are identical. Kant believes that his argument for the equality of the formulas is analytical, and
if he is correct, it should be possible to recreate the argument in logic.%
\end{isamarkuptext}\isamarkuptrue%
%
\isadelimdocument
%
\endisadelimdocument
%
\isatagdocument
%
\isamarkupsection{Definition of a Maxim%
}
\isamarkuptrue%
%
\endisatagdocument
{\isafolddocument}%
%
\isadelimdocument
%
\endisadelimdocument
%
\begin{isamarkuptext}%
The central unit of evaluation for the universalizability test is a ``maxim," which Kant defines 
in a footnote in \emph{Groundworkd} as ``the subjective principle of willing," or the principle that 
the agent acts on \cite[16]{groundwork}. Modern Kantians differ in their interpretations of this definition. The naive view 
is that a maxim is an act, but Korsgaard adopts the more sophisticated view that a maxim is composed
of an act and the agent's purpose for acting \cite{actingforareason}. She also compares a maxim 
to Aristotle's logos, which includes these components and information about the circumstances and methods 
of the act. O'Neill concludes that Kant's examples imply that a maxim must also include circumstances \cite{actingonprinciple}, and 
Kitcher \cite{whatisamaxim} uses textual evidence from the Groundwork to argue for the inclusion of a maxim's purpose 
or motivation. In order to formalize the notion of a maxim, I must adopt a specific definition and 
defend my choice.

@@

The practical contradiction interpretation not only addresses the problems with the first two 
interpretations, it also offers a much more satisfying explanation of why certain maxims are immoral. 
The problem is not the existence of a contradiction itself, but instead the fact that these maxims 
involve parasitic behavior on social conditions that the agent seeks to benefit from. The false promiser 
simultaneously wants to abuse the system of promising and benefit from it, and is thus making an exception 
of themselves. It is this kind of free-riding that the universalizability test seeks to draw out. The test
raises the same kinds of objections that the question ``What if everyone did that?" seeks to draw out.%
\end{isamarkuptext}\isamarkuptrue%
%
\isadelimtheory
%
\endisadelimtheory
%
\isatagtheory
%
\endisatagtheory
{\isafoldtheory}%
%
\isadelimtheory
%
\endisadelimtheory
%
\end{isabellebody}%
\endinput
%:%file=~/Desktop/cs91r/paper/threeflags.thy%:%
%:%24=9%:%
%:%36=12%:%
%:%37=13%:%
%:%38=14%:%
%:%39=15%:%
%:%40=16%:%
%:%41=17%:%
%:%42=18%:%
%:%43=19%:%
%:%44=20%:%
%:%45=21%:%
%:%46=22%:%
%:%47=23%:%
%:%48=24%:%
%:%49=25%:%
%:%50=26%:%
%:%51=27%:%
%:%52=28%:%
%:%53=29%:%
%:%54=30%:%
%:%55=31%:%
%:%56=32%:%
%:%57=33%:%
%:%58=34%:%
%:%59=35%:%
%:%60=36%:%
%:%61=37%:%
%:%62=38%:%
%:%63=39%:%
%:%64=40%:%
%:%65=41%:%
%:%66=42%:%
%:%67=43%:%
%:%68=44%:%
%:%69=45%:%
%:%70=46%:%
%:%71=47%:%
%:%72=48%:%
%:%73=49%:%
%:%74=50%:%
%:%75=51%:%
%:%76=52%:%
%:%77=53%:%
%:%78=54%:%
%:%79=55%:%
%:%80=56%:%
%:%81=57%:%
%:%82=58%:%
%:%83=59%:%
%:%84=60%:%
%:%85=61%:%
%:%86=62%:%
%:%87=63%:%
%:%88=64%:%
%:%97=66%:%
%:%109=68%:%
%:%110=69%:%
%:%111=70%:%
%:%112=71%:%
%:%113=72%:%
%:%114=73%:%
%:%115=74%:%
%:%116=75%:%
%:%117=76%:%
%:%118=77%:%
%:%119=78%:%
%:%120=79%:%
%:%121=80%:%
%:%122=81%:%
%:%123=82%:%
%:%124=83%:%
%:%125=84%:%
%:%126=85%:%
%:%127=86%:%
%:%128=87%:%
%:%129=88%:%
%:%130=89%:%
%:%139=91%:%
%:%151=93%:%
%:%152=94%:%
%:%153=95%:%
%:%154=96%:%
%:%155=97%:%
%:%156=98%:%
%:%157=99%:%
%:%158=100%:%
%:%159=101%:%
%:%160=102%:%
%:%161=103%:%
%:%162=104%:%
%:%163=105%:%
%:%164=106%:%
%:%165=107%:%
%:%166=108%:%
%:%167=109%:%
%:%168=110%:%
%:%169=111%:%
%:%170=112%:%
%:%171=113%:%
%:%172=114%:%
%:%173=115%:%
%:%174=116%:%
%:%175=117%:%
%:%176=118%:%
%:%177=119%:%
%:%178=120%:%
%:%179=121%:%
%:%180=122%:%
%:%181=123%:%
%:%182=124%:%
%:%183=125%:%
%:%184=126%:%
%:%185=127%:%
%:%186=128%:%
%:%187=129%:%
%:%188=130%:%
%:%189=131%:%
%:%190=132%:%
%:%191=133%:%
%:%192=134%:%
%:%193=135%:%
%:%194=136%:%
%:%195=137%:%
%:%196=138%:%
%:%197=139%:%
%:%198=140%:%
%:%199=141%:%
%:%200=142%:%
%:%201=143%:%
%:%202=144%:%
%:%211=146%:%
%:%223=148%:%
%:%224=149%:%
%:%225=150%:%
%:%226=151%:%
%:%227=152%:%
%:%228=153%:%
%:%229=154%:%
%:%230=155%:%
%:%231=156%:%
%:%232=157%:%
%:%233=158%:%
%:%234=159%:%
%:%235=160%:%
%:%236=161%:%
%:%237=162%:%
%:%238=163%:%
%:%239=164%:%
%:%240=165%:%
%:%241=166%:%
%:%242=167%:%
%:%243=168%:%
%:%244=169%:%
%:%245=170%:%
%:%254=172%:%
%:%266=174%:%
%:%267=175%:%
%:%268=176%:%
%:%269=177%:%
%:%270=178%:%
%:%271=179%:%
%:%272=180%:%
%:%273=181%:%
%:%274=182%:%
%:%275=183%:%
%:%276=184%:%
%:%277=185%:%
%:%278=186%:%
%:%279=187%:%
%:%280=188%:%
%:%281=189%:%
%:%282=190%:%
%:%283=191%:%
%:%284=192%:%
%:%285=193%:%
%:%286=194%:%
%:%287=195%:%
%:%288=196%:%
%:%289=197%:%
%:%290=198%:%
%:%291=199%:%
%:%292=200%:%
%:%293=201%:%
%:%294=202%:%
%:%295=203%:%
%:%296=204%:%
%:%297=205%:%
%:%298=206%:%
%:%299=207%:%
%:%300=208%:%
%:%301=209%:%
%:%302=210%:%
%:%303=211%:%
%:%304=212%:%
%:%305=213%:%
%:%306=214%:%
%:%307=215%:%
%:%308=216%:%
%:%309=217%:%
%:%310=218%:%
%:%311=219%:%
%:%312=220%:%
%:%313=221%:%
%:%314=222%:%
%:%315=223%:%
%:%316=224%:%
%:%317=225%:%
%:%318=226%:%

>>>>

Though Kantians study all formulations of the categorical imperative, Kant argues in Groundwork 
that the three formulations of the categorical imperative are equivalent \cite{groundwork}. While this 
argument is disputed \cite{sepkant}, for those who believe it, the
stakes for my choice of the FUL are greatly reduced. If all formulations are equivalent, then a formalization of the FUL
lends the exact same power as a formalization of the second or third formulation of the categorical 
imperative. In fact, future work could formalize the other formulas and try to prove that they 
are identical. Kant believes that his argument for the equality of the formulas is analytical, and
if he is correct, it should be possible to recreate the argument in logic.

Those who do not believe that all three formulations of the categorical imperative are equivalent may
understand the FUL as the strongest or most foundational, and thus an appropriate initial choice for 
formalizations. Korsgaard characterizes the three formulations of the categorical
imperative according to Rawls' general and special conception of justice. The general conception applies
universally and can never be violated and the special conception represents an ideal for us to
live towards. For example, the special conception may require that we prefer some job applicants
over others in order to remedy historical injustice, and the general conception may require that such
inequalities always operate in the service of the least privileged \citep[19]{KorsgaardRTL}. Korsgaard
argues that the Formula of Universal Law represents Kant's general conception of justice, and the Formula of 
Humanity represents his special conception. The FUL's prescriptions can never be violated, even in the most
non-ideal circumstances imaginable, but the FUH is merely a standard to live towards that might not be 
achieved. In this sense, the FUL generates stronger requirements than the other two formulations and is 
thus the bare minimum of Kant's ethics. Because the FUL's prescriptions outweigh those of the other two formulations,
formalizing it creates a functional, minimum ethical theory that can serve as a foundation for implementations
of other aspects of Kant's ethics.%
\end{isamarkuptext}\isamarkuptrue%
%
\isadelimdocument
%
\endisadelimdocument
%
\isatagdocument
%
\isamarkupsection{Definition of a Maxim%
}
\isamarkuptrue%
%
\endisatagdocument
{\isafolddocument}%
%
\isadelimdocument
%
\endisadelimdocument
%
\begin{isamarkuptext}%
The central unit of evaluation for the universalizability test is a ``maxim," which Kant defines 
in a footnote in \emph{Groundworkd} as ``the subjective principle of willing," or the principle that 
the agent acts on \cite[16]{groundwork}. Modern Kantians differ in their interpretations of this definition. The naive view 
is that a maxim is an act, but Korsgaard adopts the more sophisticated view that a maxim is composed
of an act and the agent's purpose for acting \cite{actingforareason}. She also compares a maxim 
to Aristotle's logos, which includes these components and information about the circumstances and methods 
of the act. O'Neill concludes that Kant's examples imply that a maxim must also include circumstances \cite{actingonprinciple}, and 
Kitcher \cite{whatisamaxim} uses textual evidence from the Groundwork to argue for the inclusion of a maxim's purpose 
or motivation. In order to formalize the notion of a maxim, I must adopt a specific definition and 
defend my choice.

@@

The practical contradiction interpretation not only addresses the problems with the first two 
interpretations, it also offers a much more satisfying explanation of why certain maxims are immoral. 
The problem is not the existence of a contradiction itself, but instead the fact that these maxims 
involve parasitic behavior on social conditions that the agent seeks to benefit from. The false promiser 
simultaneously wants to abuse the system of promising and benefit from it, and is thus making an exception 
of themselves. It is this kind of free-riding that the universalizability test seeks to draw out. The test
raises the same kinds of objections that the question ``What if everyone did that?" seeks to draw out.%
\end{isamarkuptext}\isamarkuptrue%
%
\isadelimtheory
%
\endisadelimtheory
%
\isatagtheory
%
\endisatagtheory
{\isafoldtheory}%
%
\isadelimtheory
%
\endisadelimtheory
%
\end{isabellebody}%
\endinput
%:%file=~/Desktop/cs91r/paper/threeflags.thy%:%
%:%24=9%:%
%:%36=12%:%
%:%37=13%:%
%:%38=14%:%
%:%39=15%:%
%:%40=16%:%
%:%41=17%:%
%:%42=18%:%
%:%43=19%:%
%:%44=20%:%
%:%45=21%:%
%:%46=22%:%
%:%47=23%:%
%:%48=24%:%
%:%49=25%:%
%:%50=26%:%
%:%51=27%:%
%:%52=28%:%
%:%53=29%:%
%:%54=30%:%
%:%55=31%:%
%:%56=32%:%
%:%57=33%:%
%:%58=34%:%
%:%59=35%:%
%:%60=36%:%
%:%61=37%:%
%:%62=38%:%
%:%63=39%:%
%:%64=40%:%
%:%65=41%:%
%:%66=42%:%
%:%67=43%:%
%:%68=44%:%
%:%69=45%:%
%:%70=46%:%
%:%71=47%:%
%:%72=48%:%
%:%73=49%:%
%:%74=50%:%
%:%75=51%:%
%:%76=52%:%
%:%77=53%:%
%:%78=54%:%
%:%79=55%:%
%:%80=56%:%
%:%81=57%:%
%:%82=58%:%
%:%83=59%:%
%:%84=60%:%
%:%85=61%:%
%:%86=62%:%
%:%87=63%:%
%:%88=64%:%
%:%89=65%:%
%:%90=66%:%
%:%91=67%:%
%:%92=68%:%
%:%93=69%:%
%:%94=70%:%
%:%95=71%:%
%:%96=72%:%
%:%97=73%:%
%:%98=74%:%
%:%99=75%:%
%:%100=76%:%
%:%101=77%:%
%:%102=78%:%
%:%103=79%:%
%:%104=80%:%
%:%113=82%:%
%:%125=84%:%
%:%126=85%:%
%:%127=86%:%
%:%128=87%:%
%:%129=88%:%
%:%130=89%:%
%:%131=90%:%
%:%132=91%:%
%:%133=92%:%
%:%134=93%:%
%:%135=94%:%
%:%136=95%:%
%:%137=96%:%
%:%138=97%:%
%:%139=98%:%
%:%140=99%:%
%:%141=100%:%
%:%142=101%:%
%:%143=102%:%
%:%144=103%:%
%:%145=104%:%
%:%146=105%:%
%:%155=107%:%
%:%167=109%:%
%:%168=110%:%
%:%169=111%:%
%:%170=112%:%
%:%171=113%:%
%:%172=114%:%
%:%173=115%:%
%:%174=116%:%
%:%175=117%:%
%:%176=118%:%
%:%177=119%:%
%:%178=120%:%
%:%179=121%:%
%:%180=122%:%
%:%181=123%:%
%:%182=124%:%
%:%183=125%:%
%:%184=126%:%
%:%185=127%:%
%:%186=128%:%
%:%187=129%:%
%:%188=130%:%
%:%189=131%:%
%:%190=132%:%
%:%191=133%:%
%:%192=134%:%
%:%193=135%:%
%:%194=136%:%
%:%195=137%:%
%:%196=138%:%
%:%197=139%:%
%:%198=140%:%
%:%199=141%:%
%:%200=142%:%
%:%201=143%:%
%:%202=144%:%
%:%203=145%:%
%:%204=146%:%
%:%205=147%:%
%:%206=148%:%
%:%207=149%:%
%:%208=150%:%
%:%209=151%:%
%:%210=152%:%
%:%211=153%:%
%:%212=154%:%
%:%213=155%:%
%:%214=156%:%
%:%215=157%:%
%:%216=158%:%
%:%217=159%:%
%:%218=160%:%
%:%227=162%:%
%:%239=164%:%
%:%240=165%:%
%:%241=166%:%
%:%242=167%:%
%:%243=168%:%
%:%244=169%:%
%:%245=170%:%
%:%246=171%:%
%:%247=172%:%
%:%248=173%:%
%:%249=174%:%
%:%250=175%:%
%:%251=176%:%
%:%252=177%:%
%:%253=178%:%
%:%254=179%:%
%:%255=180%:%
%:%256=181%:%
%:%257=182%:%
%:%258=183%:%
%:%259=184%:%
%:%260=185%:%
%:%261=186%:%
%:%270=188%:%
%:%282=190%:%
%:%283=191%:%
%:%284=192%:%
%:%285=193%:%
%:%286=194%:%
%:%287=195%:%
%:%288=196%:%
%:%289=197%:%
%:%290=198%:%
%:%291=199%:%
%:%292=200%:%
%:%293=201%:%
%:%294=202%:%
%:%295=203%:%
%:%296=204%:%
%:%297=205%:%
%:%298=206%:%
%:%299=207%:%
%:%300=208%:%
%:%301=209%:%
%:%302=210%:%
%:%303=211%:%
%:%304=212%:%
%:%305=213%:%
%:%306=214%:%
%:%307=215%:%
%:%308=216%:%
%:%309=217%:%
%:%310=218%:%
%:%311=219%:%
%:%312=220%:%
%:%313=221%:%
%:%314=222%:%
%:%315=223%:%
%:%316=224%:%
%:%317=225%:%
%:%318=226%:%
%:%319=227%:%
%:%320=228%:%
%:%321=229%:%
%:%322=230%:%
%:%323=231%:%
%:%324=232%:%
%:%325=233%:%
%:%326=234%:%
%:%327=235%:%
%:%328=236%:%
%:%329=237%:%
%:%330=238%:%
%:%331=239%:%
%:%332=240%:%
%:%333=241%:%
%:%334=242%:%
